### 2025-06-06 short/sections/future-papers.tex
Update future-papers.tex

\begin{benumerate}{8}

\item{González-Bustamante, B. (2025, {\itshape second round}). Blame-Shifting in Presidential Systems: Corrective Effect of Ministerial Terminations on Approval. Preprint upon request.}\vspace{1mm}

\item{Kantorowicz, J., \& González-Bustamante, B. (2025, {\itshape second round}). Changing Meaning of the Rule of Law. OSF preprint. DOI: \href{https://doi.org/10.31219/osf.io/2kzpj}{\textcolor{blue}{10.31219/osf.io/2kzpj}}.}\vspace{1mm}

\item{Kantorowicz, J., \& González-Bustamante, B. (2025, {\itshape second round}). Exploring the Rule of Law in Academic Discourse: A Comprehensive Bibliometric Analysis. OSF preprint. DOI: \href{https://doi.org/10.31219/osf.io/sgf8y}{\textcolor{blue}{10.31219/osf.io/sgf8y}}.}\vspace{1mm}

\item{DiGiuseppe, M., Aspide, A., Kantorowicz, J. \& González-Bustamante, B. (2025, {\itshape first round}). Putting the Public Back in Public Debt: Citizen Narratives on Public Debt Burdens.Preprint upon request.}\vspace{1mm}

@@

\item{Orchard, X., González-Bustamante, B., \& Cisternas. C. (2024, {\itshape first round}). Amplification, Contestation, and Toxic Interactions with News: Testing the Effect of a Protest Cycle in Digital News Participation. Preprint upon request.}\vspace{1mm}

>>>>

\begin{benumerate}{6}

\item{Orchard, X., González-Bustamante, B., \& Cisternas, C. (2025, {\itshape second round}). Amplification, Contestation, and Toxic Interactions with News: Testing the Effect of a Protest Cycle in Digital News Participation. Preprint upon request.}\vspace{1mm}

\item{DiGiuseppe, M., Aspide, A., Kantorowicz, J., \& González-Bustamante, B. (2025, {\itshape second round}). Putting the Public Back in Public Debt: Citizen Narratives on Public Debt Burdens. Preprint upon request.}\vspace{1mm}

\item{Kantorowicz, J., \& González-Bustamante, B. (2024, {\itshape first round}). Exploring the Rule of Law in Academic Discourse: A Comprehensive Bibliometric Analysis. OSF preprint. DOI: \href{https://doi.org/10.31219/osf.io/sgf8y}{\textcolor{blue}{10.31219/osf.io/sgf8y}}.}\vspace{1mm}

@@
